Tabular Constraint Learning

### 2016-04-12 Paper/ECAI/tabular.tex
Fixed table
rank

\documentclass{ecai}
\usepackage{times}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{xspace}
\usepackage{hyperref}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[numbers]{natbib}
\usepackage{notoccite}
\usepackage{framed}
\usepackage{amsmath}

@@

\begin{table*}
  \centering
  \begin{tabular}{ccc}
    \textbf{\CName} & \textbf{\CSignature} & \textbf{\CFunction}\\
    ALLDIFFERENT(X) & X is integer or textual & All elements in X are different \\
    %X = Y & & \\
    FK $\rightarrow$ PK & FK and PK have the same type; they originate from different tables and PK is all-different & all values in FK exist in PK \\
    % TODO check out
    R = LOOKUP-PRODUCT(FV, FK=PK, PV) & & \\
    FV = FUZZY-LOOKUP(FK, PK, PV) & & \\
    FV = LOOKUP(FK, PK, PV) & & \\
    PERMUTATION(X) & & \\
    R = O1 * O2 & & \\
    R = PROJECT(P) & & \\
     Y = RANK(X) & & \\
    A = PREV(A) + P - N & A, P and N have the same length and their length is at least 2 & *\\
    SERIES(X) & & \\
    Y = SUM(X, col) & & Y is the result of summing each column in X \\
    Y = SUM(X, row) & & Y is the result of summing each row in X \\
    R = SUMIF(FK=PK, V) & & \\
    R = SUMPRODUCT(O1, O2) & & \\

@@

  \end{tabular}
  \caption{Excel Tabular Constraints \sergey{Luc, we need your comments here on the notation of $X,Y$ and $G_X,G_Y$}}
  \label{table:constraints}
\end{table*}

>>>>

\documentclass{ecai}
\usepackage{times}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{xspace}
\usepackage{hyperref}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[numbers]{natbib}
\usepackage{notoccite}
\usepackage{framed}
\usepackage{amsmath}
\usepackage{tabularx}

@@

\begin{table*}
  \centering
  \begin{tabularx}{\textwidth}{XXX}
    \textbf{\CName} & \textbf{\CSignature} & \textbf{\CFunction}\\
    ALLDIFFERENT(X) & X is integer or textual & All elements in X are different \\
    %X = Y & & \\
    FK $\rightarrow$ PK & FK and PK have the same type; they originate from different tables and PK is all-different & all values in FK exist in PK \\
    % TODO check out
    R = LOOKUP-PRODUCT(FV, FK=PK, PV) & & \\
    FV = FUZZY-LOOKUP(FK, PK, PV) & & \\
    FV = LOOKUP(FK, PK, PV) & & \\
    PERMUTATION(X) & & \\
    R = O1 * O2 & & \\
    R = PROJECT(P) & & \\
    Y = RANK(X) & Y and X have the same length & Y is the rank of X (including ties)\\
    A = PREV(A) + P - N & A, P and N have the same length and their length is at least 2 & *\\
    SERIES(X) & & \\
    Y = SUM(X, col) & & Y is the result of summing each column in X \\
    Y = SUM(X, row) & & Y is the result of summing each row in X \\
    R = SUMIF(FK=PK, V) & & \\
    R = SUMPRODUCT(O1, O2) & & \\

@@

  \end{tabularx}
  \caption{Excel Tabular Constraints \sergey{Luc, we need your comments here on the notation of $X,Y$ and $G_X,G_Y$}}
  \label{table:constraints}
\end{table*}
